---
title: "exercise"
author: "ffmustbe"
date: '2022-10-18'
output:
  pdf_document: default
  html_document: default
---
```{r}
usethis::create_github_token()
```



```{r setup, include=FALSE}
library(dplyr)
library(ggplot2)
wbdata <- jsonlite::fromJSON(gzcon(url("https://github.com/cjbarrie/CS-ED/blob/main/data/web_historian_data.json?raw=true")))
wbdata_short <- wbdata %>%
  select(domain, searchTerms, urlId)
wbdata %>%
  group_by(domain) %>%
  count()
wbdata %>%
  group_by(domain) %>%
  count() %>%
  arrange(desc(n))
wbdata_mp <- wbdata %>%
  group_by(domain) %>%
  count() %>%
  filter(n>5)
wbdata_mp %>%
  ggplot() +
  geom_bar(aes(domain,n), stat="identity") +
  coord_flip()
```
##1.Count the types of things I’m doing online (column “transType” in the wbdata). What is my most frequent type of interaction with the web?
```{r}
wbdata %>%
  group_by(transType) %>%
  count()
```
##Change the colour of the bars in the bar graph.
```{r}
wbdata_mp %>%
  ggplot() +
  geom_bar(mapping = aes(x = domain, y = n, fill = domain),stat="identity")+
  coord_flip()
```
##igraph
```{r}
library(igraph)
library(tidygraph)
library(dplyr)
library(RColorBrewer)
library(classInt)
nodes <- read.table(url("https://github.com/cjbarrie/CS-ED/blob/main/data/all.nodes.txt?raw=true"))
edges <- read.table(url("https://github.com/cjbarrie/CS-ED/blob/main/data/all.edgelist.txt?raw=true"))
```
##change the name of column 
```{r}
install.packages("tidylog",  repos = "http://cran.us.r-project.org")
library(tidylog)
colnames(nodes) <- c("node1","lr")
colnames(edges) <- c("node1", "node2", "type", "n", "id")
rt_samp <- edges %>%
  left_join(nodes, by = "node1") %>%
  filter(type == "retweet")

rt_samp$node1 <- as.character(rt_samp$node1)
rt_samp$node2 <- as.character(rt_samp$node2)
```
#matrix-character-igraph
```{r}
igraph_rt_samp <- graph_from_edgelist(
  as.matrix(rt_samp[,c("node1","node2")]),
  directed = T
)
class(igraph_rt_samp)
plot(simplify(igraph_rt_samp), 
     vertex.label = NA, 
     vertex.size = 2,
     edge.arrow.size = 0)
```
#sample
```{r}
samp_attr <- data.frame(
  node = V(igraph_rt_samp)$name,
  node.seq = 1:length(V(igraph_rt_samp)$name),
  degree.in = degree(igraph_rt_samp, mode = "in"), #unhash this to also estimate indegree
  between.dir = betweenness(igraph_rt_samp, directed = T,normalized = T), #unhash this to also estimate betweenness
  between.undir = betweenness(igraph_rt_samp, directed = F, normalized = T) #unhash this to also estimate betweenness (undirected)
)
```

```{r}
nodes$node <- as.character(nodes$node)
nodes <- nodes %>%
  mutate(lrcolor = recode(lr,
                          "right" = "#DE0100",
                          "left" = "#0015BC",
                          "-" = "#a6a49f")
  )
samp_attr_lr <- samp_attr %>%
  left_join(nodes, by = "node")
plot(simplify(igraph_rt_samp), 
     vertex.label = NA, 
     vertex.size = 4,
     vertex.color = samp_attr_lr$lrcolor,
     edge.arrow.size = 0)
```

##Count how many “left” nodes there are and how many “right” nodes there are.
```{r}
table(nodes$lr)
```
##Add arrows to the network plot and increase their width
```{r}

plot(simplify(igraph_rt_samp), 
     vertex.label = NA, 
     vertex.size = 4,
     vertex.color = samp_attr_lr$lrcolor,
     edge.arrow.width=0.5,
     edge.arrow.size = 0.3)

```

